\Title

### 2021-01-26 manuscript/manuscript.tex

The vertical component of the gravitational acceleration generated by the
model was computed  using the method of \citet{nagy2000, nagy2002}
with recent modifications by \citet{fukushima2020},
as implemented in the open-source software Harmonica \citep{harmonica}.
We generated a \emph{target grid} of
\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
\TargetSpacing{} and located \TargetHeight{} above the zero height plane
(Fig.~\ref{fig:synthetic-target}) to serve as a reference when calculating the
interpolation error.
We then generated synthetic ground (Fig.~\ref{fig:synthetic-layouts}b) and
airborne (Fig.~\ref{fig:synthetic-layouts}d) data to which we added
pseudo-random Gaussian noise with zero mean and \SurveyNoise{} standard
deviation.

@@

>>>>

The vertical component of the gravitational acceleration generated by the
model was computed  using the method of \citet{nagy2000, nagy2002}
with recent modifications by \citet{fukushima2020},
as implemented in the open-source software Harmonica \citep{harmonica2020}.
We generated a \emph{target grid} of
\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
\TargetSpacing{} and located \TargetHeight{} above the zero height plane
(Fig.~\ref{fig:synthetic-target}) to serve as a reference when calculating the
interpolation error.
We then generated synthetic ground (Fig.~\ref{fig:synthetic-layouts}b) and
airborne (Fig.~\ref{fig:synthetic-layouts}d) data to which we added
pseudo-random Gaussian noise with zero mean and \SurveyNoise{} standard
deviation.

@@

\section{Software implementation}

We have implemented the methods described in the previous sections though
a software written in Python language.
The code for generating the results of this work are available in
\url{https://doi.org/10.6084/m9.figshare.13604360} or
\url{https//github.com/compgeolab/eql-gradient-boosted}.
The gradient-boosted equivalent sources implementation is based on the
non-boosted sources available through the Harmonica library
\citep{harmonica2020}, part of the Fatiando a Terra project
\citep{fatiando2013}.
Another Python libraries were used:
Verde \citep{verde2018} to apply block reductions and managing coordinates,
Boule \citep{boule2020} for computing normal gravity,
Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
multidimensional datasets and numerical
computations,
Numba \citep{numba2015} for writing pre-comipled implementations and
parallelization,
Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
the figures.
